Associations of environmental and human factors with altered rodent populations in West Africa: A scoping review

### 2021-04-23 reports/manuscript.Rmd
change to more detailed map

``` {r density, fig.cap = "Density of trap sites per thousand km^2^", echo = F, layout = "l-page"}
knitr::include_graphics(here::here("figures", "static_site_density.png"))
```

>>>>

``` {r density, fig.cap = "Density of trap sites per thousand km^2^", echo = F, layout = "l-page"}
knitr::include_graphics(here::here("figures", "static_site_density_2.png"))
```
